---
title: "Regression_miHuron"
author: "S M Nazarat Hossain"
date: "February 25, 2020"
output: html_document
---


```{r, warning=FALSE, message=FALSE}
# Loading library
library(xts)
library(forecast)
library(forecast)
library(tseries)
library(TSA)
library(knitr)
```
```{r}
dataPath <- 'C:/Users/nazar/Desktop/Project_time_series/'
dat <- read.csv(paste0(dataPath,'Data_V3.csv'),header = T)
head(dat)
```


```{r}
ts.dat=ts(dat,frequency = 12, start = c(1918,1))
head(ts.dat)
```

# Splitting data

Split data into train and test dataset
```{r}
tsreg.train<-window(ts.dat,start=c(1950,1),end=c(2015,12))
tsreg.test<-window(ts.dat,start=c(2016,1),end=c(2019,12))
```


# Arimax model 


```{r}
tsreg.sarima60 <- arimax(tsreg.train[,"water_levels"], xreg = tsreg.train[,c("sea_level_changes", 
                     "airTemp_overlake", "airTemp_overland", "precipitation_depth_overland",        "precipitation_depth_overlake")], order=c(1,1,1), seasonal = c(1,0,1))
summary(tsreg.sarima60)
checkresiduals(tsreg.sarima60)
```


```{r}
#tsreg.sarima60 <- Arima(tsreg.test[,"water_levels"], model=tsreg.sarima61, xreg=tsreg.test[,c(4:8)])
fcast.tsreg.sarima60<-forecast(tsreg.sarima60, xreg=tsreg.test[,c(4:8)])
plot(fcast.tsreg.sarima60)

```

```{r}

ts.plot(data.frame(tsreg.test)$water_levels,fcast.tsreg.sarima60$mean, col = c("red", "blue"))
legend("topleft", bty="n", lty=c(1,1), col=c("red","blue"),
       legend=c(" Test ", "Forecast"))
```


Prf Rob J Hyndman: To apply a model to a new data set, first construct the model object, then forecast. Like this

fit2 <- Arima(dat[,2], model=fit, xreg=dat[,-1])
forecast(fit2, xreg=ex)

# Plot Armax model

```{r}
tsreg.sarima61 <- Arima(tsreg.train[,"water_levels"], xreg = tsreg.train[,c("sea_level_changes", 
                     "airTemp_overlake", "airTemp_overland", "precipitation_depth_overland",                    "precipitation_depth_overlake")], order=c(1,1,1), seasonal = c(1,0,1))
summary(tsreg.sarima61)
checkresiduals(tsreg.sarima61)
```
```{r}

fcast.tsreg.sarima61<-forecast(tsreg.sarima61, xreg=tsreg.test[,c(4:8)])
plot(fcast.tsreg.sarima61)
```
```{r}

ts.plot(data.frame(tsreg.test)$water_levels,fcast.tsreg.sarima61$mean, col = c("red", "blue"))
legend("topleft", bty="n", lty=c(1,1), col=c("red","blue"),
       legend=c(" Test ", "Forecast"))
```


```{r}
tsreg.sarima62 <- arimax(tsreg.train[,"water_levels"], xreg = tsreg.train[,c("sea_level_changes", 
                     "airTemp_overlake", "airTemp_overland", "precipitation_depth_overland",                        "precipitation_depth_overlake")], order=c(1,1,1), seasonal = c(1,0,1))
summary(tsreg.sarima62)
checkresiduals(tsreg.sarima62)
```

Coefficients:
         ar1      ma1    sar1     sma1  sea_level_changes  airTemp_overlake  airTemp_overland
      0.5220  -0.0224  0.9998  -0.9845             0.0201            0.0038             6e-04
s.e.  0.0662   0.0805  0.0004   0.0166             0.0014            0.0013             5e-04
      precipitation_depth_overland  precipitation_depth_overlake
                             1e-04                         0e+00
s.e.                         1e-04                         1e-04

sigma^2 estimated as 0.001324:  log likelihood=1497.53
AIC=-2975.05   AICc=-2974.77   BIC=-2928.32

Training set error measures:
                        ME      RMSE        MAE         MPE       MAPE      MASE        ACF1
Training set -0.0005432214 0.0361507 0.02785781 -0.00030563 0.01578516 0.1358663 0.005327611

	Ljung-Box test

data:  Residuals from Regression with ARIMA(1,1,1)(1,0,1)[12] errors
Q* = 21.108, df = 15, p-value = 0.1334

Model df: 9.   Total lags used: 24


```{r}
tsreg.sarima63 <- Arima(tsreg.train[,"water_levels"], xreg = tsreg.train[,c("sea_level_changes", 
                     "airTemp_overlake", "airTemp_overland", "precipitation_depth_overland",                        "precipitation_depth_overlake")], order=c(1,1,1), seasonal = c(1,0,1))
summary(tsreg.sarima63)
checkresiduals(tsreg.sarima63)
```



# sarima regression model with d=1, D=1, and lambda = 1


```{r}
tsreg.sarima25 <- auto.arima(tsreg.train[,"water_levels"], xreg = tsreg.train[,c("sea_level_changes", 
                     "airTemp_overlake", "airTemp_overland", "precipitation_depth_overland",                                    "precipitation_depth_overlake") ], d=1, D=1,lambda = 1)

summary(tsreg.sarima25)
checkresiduals(tsreg.sarima25)
```





```{r}

fcast.tsreg.sarima25<-forecast(tsreg.sarima25, xreg=tsreg.test[,c(4:8)])
plot(fcast.tsreg.sarima25)
```
```{r}

ts.plot(data.frame(tsreg.test)$water_levels,fcast.tsreg.sarima25$mean, col = c("red", "blue"))
legend("topleft", bty="n", lty=c(1,1), col=c("red","blue"),
       legend=c(" Test ", "Forecast"))
```

